---
title: "Using IDEAFilter"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using IDEAFilter}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(IDEAFilter)
```

# Minimal Example

Here is a minimal example using `IDEAFilter_ui()` and `IDEAFilter()` to explore a dataset:
```{r, eval=FALSE}
library(shiny)
library(IDEAFilter)
library(dplyr)
shinyApp(
  ui = fluidPage(
    titlePanel("Filter Data Example"),
    fluidRow(
      column(8, dataTableOutput("data_summary")),
      column(4, IDEAFilter_ui("data_filter")))),
  server = function(input, output, session) {
    filtered_data <- IDEAFilter("data_filter", data = iris, verbose = FALSE)
    output$data_summary <- 
      renderDataTable(filtered_data(), 
    options = list(scrollX = TRUE, pageLength = 5))
  }
)
```
The server side of the module returns the reactive `ShinyDataFilter_df` object which includes the filtered data frame and the code used to filter it as an attribute.

# A Larger Example

With the release of `IDEAFilter()` to replace the deprecated `shiny_data_filter()`, a couple more arguments have been introduced to enhance the functionality of the filter.

* Column Sub-setting: you can now restrict the columns a user can add to the filter.
* Pre-selection: you can now pre-specify a collection of filters to either pre-load in the filter or for users to dynamically apply.

To explore these features we can run the following example application:

```{r, eval=FALSE}
app <- system.file("examples", "starwars_app", package = "IDEAFilter")
runApp(app)
```